Summary of COVID-19 Cases in Toronto

### 2021-01-29 outputs/paper/paper.Rmd
Rmd updates

---
title: "Summary of COVID-19 Cases in Toronto"
subtitle: "Examine Trend of COVID-19 Cases"
author: "Xinyi Xu"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "https://github.com/xuxinyi720/Assignment1.git"
abstract: "COVID-19 has been recognized as a global threat; thus, numerous studies have been conducted in order to control and prevent this pandemic. I am going to use the dataset from Toronto Public Healthto summarize and analyze data to find how the pandemic is evolving, and assess severity and risk in Toronto. It is crucial for the Ministry of Health and our local public health institution to have an in-depth understanding of the disease and develop the necessary interventions to prevent further spread."
output:
  bookdown::pdf_document2:
fontfamily: mathpazo
fontsize: 30pt
toc: FALSE
bibliography: references.bib
---

@@

\newpage
# References

>>>>

---
title: "Summary of COVID-19 Cases in Toronto"
subtitle: "Examine Trend of COVID-19 Cases"
author: "Xinyi Xu"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "https://github.com/xuxinyi720/Assignment1.git"
abstract: "COVID-19 has been recognized as a global threat; thus, numerous studies have been conducted in order to control and prevent this pandemic. I am going to use the dataset from Toronto Public Healthto summarize and analyze data to find how the pandemic is evolving, and assess severity and risk in Toronto. It is crucial for the Ministry of Health and our local public health institution to have an in-depth understanding of the disease and develop the necessary interventions to prevent further spread."
output:
  bookdown::pdf_document2:
fontfamily: mathpazo
fontsize: 20pt
toc: FALSE
bibliography: references.bib
---

@@

\newpage
# References
=======
---
title: "Summary of COVID-19 Cases in Toronto"
subtitle: "Examine Trend of COVID-19 Cases"
author: "Xinyi Xu"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "https://github.com/xuxinyi720/Assignment1.git"
abstract: "COVID-19 has been recognized as a global threat; thus, numerous studies have been conducted in order to control and prevent this pandemic. I am going to use the dataset from Toronto Public Healthto summarize and analyze data to find how the pandemic is evolving, and assess severity and risk in Toronto. It is crucial for the Ministry of Health and our local public health institution to have an in-depth understanding of the disease and develop the necessary interventions to prevent further spread."
output:
  bookdown::pdf_document2:
fontfamily: mathpazo
fontsize: 30pt
toc: FALSE
bibliography: references.bib
---

\newpage
# References
>>>>>>> fac587325dcfcdf4c1f0ad2fc37cb99888d87ee6
